Figures

### 2020-01-08 manuscript/figures.Rmd
cleanup
add figures showing initial modelling results

```{r contrasts_tally, fig.cap = "Number of lakes by categories.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_contrasts_tally-1.pdf")
```

@@

@@

>>>>

```{r glaciated_vs_shapeclass, fig.cap = "Cross tabulation between lake glaciation and shape class. Circles are proportional to the number of lakes in each category. If a lake has been glaciated it is more likely to be convex. However, if a lake has not been glaciated there is no tendencey towards a particular shape class.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/glaciated_vs_shapeclass-1.pdf")
```

```{r contrasts_tally, fig.cap = "Number of lake depth measurements by categories.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_contrasts_tally-1.pdf")
```

```{r 01_programs_tally, fig.cap = "Number of programs by categories.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_programs_tally-1.pdf")
```

@@

```{r 02_depth_model_fitted, fig.cap = "A model that does not include shape class over predicts depth in concave lakes but does not systematically under predict depth in convex lakes.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_model_fitted-1.pdf")
```

@@

```{r 02_hypso_model_fitted, fig.cap = "Confusion matrix comparing two classification methods", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_hypso_model_fitted-1.pdf")
```

```{r 02_hypso_model_importance, fig.cap = "Recusive Partitioning variable importance.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_hypso_model_importance-1.pdf")
```
